A simulation-based assessment of the relation between Stone Age sites and relative sea-level change along the Norwegian Skagerrak coast

### 2022-02-10 analysis/paper/paper.Rmd
Re-running analyses. Alo revisiting shoreline dating. Requires an increment of 0.001m?

One of the more comprehensive evaluations of this relationship was done by Solheim and colleagues (@breivik2018; @solheim2020), who compared 102 ^14^C-dates from 33 Mesolithic sites on the western side of the Oslo fjord to the displacement curve for the Larvik area. They found an overlap between the probability density of the radiocarbon dates with the shoreline displacement curve for 86.5% of the sites. However, where there was a discrepancy, the main occupation of the sites are still believed to have been shore-bound rather than associated with the deviating ^14^C-dates. This is based on typological and technological characteristics of the assemblages. Whether these mismatches represent later shorter visits that are responsible for the younger radiocarbon dates, or whether these are entirely erroneous results of contamination can be difficult to evaluate. Here this will be entirely dependent on, and follow the discretion of the original excavation reports.

@@

# Model dates using the Boundary function
datedat <- model_dates(sitedates = siter, date_groups = date_groups)

>>>>

One of the more comprehensive evaluations of this relationship was done by Solheim and colleagues [@breivik2018; @solheim2020], who compared 102 ^14^C-dates from 33 Mesolithic sites on the western side of the Oslo fjord to the displacement curve for the Larvik area. They found an overlap between the probability density of the radiocarbon dates with the shoreline displacement curve for 86.5% of the sites. However, where there was a discrepancy, the main occupation of the sites are still believed to have been shore-bound rather than associated with the deviating ^14^C-dates. This is based on typological and technological characteristics of the assemblages. Whether these mismatches represent later shorter visits that are responsible for the younger radiocarbon dates, or whether these are entirely erroneous results of contamination can be difficult to evaluate. Here this will be entirely dependent on, and follow the discretion of the original excavation reports.

@@

# Model dates using the Boundary function in OxCal
datedat <- model_dates(sitedates = siter, date_groups = date_groups)
